### 2016-11-28 ms/ms.tex

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality represents the importance of a
space by calcuating the path lengths to other vertices (species) in
the network \citep{freeman1978centrality}. The shorter the mean path
length to other species, the higher the closeness centrality. We use
linear mixed models to test whether the species closeness variability
(log) is related to the persistence or degree of that species
\citep{lme4, lmetest}. We included random effects for species and
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.84$, $p$-value $<$ $2*10^{-16}$), we include
each explanatory variable in separate models. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency.  Because an
approximately logarithmic increase in closeness centrality, as would
be expected with assembly by preferential attachment, would also lead
to high variability in closeness scores, we also test whether log
closeness centrality increases through time.

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (Fig.~\ref{fig:cv}, estimate
of the slope of closeness centrality variability and persistence $\pm$
standard error of the estimate, $0.653 \pm 0.225$, $p$-value=$0.009$;
slope of closeness centrality variability and degree, $0.008 \pm
0.002$, $p$-value=$0.002$). The slope of these relationships remained
significant when the species with the top $10$ persistence and degree
scores were dropped. In addition, plant persistence and degree were
not significantly related to network position variability
(Fig.~\ref{fig:cv}). % estimate of the slope of closeness variability and
% persistence $\pm$ SE, $-2.063 \pm 3.091$, $p$-value=$0.5$; slope of
% closeness variability and degree, $0.0018 \pm 0.002$,
% $p$-value=$0.3$).
The variability of species network position was not the result of
closeness linearly increasing through time, and, in fact, plant and
pollinator closeness decreased slightly through time (Fig.~S2,
estimate of the slope of closeness through time $\pm$ SE, pollinators:
$-0.0003 \pm 0.00005$, $p$-value=$2.7*10^{-12}$; plants $-0.007 \pm
0.001$, $p$-value=$1.4*10^{-6}$). Through statistically significant,
the slopes are so slight they may not be biologically significant.

\subsection*{Species and interaction turnover}
The rates of plant, pollinator and interaction temporal turnover were
similar across assembling hedgerows, non-assembling hedgerows and
field margins, though mature hedgerows has marginally significantly
less pollinator turnover than field margins (Fig.~\ref{fig:beta},
estimate $\pm$ SE of the difference in turnover between field margins
and mature hedgerows, $-0.0498 \pm 0.026$, $p$-value=$0.058$). When
interactions where weighted by their similarity, both assembling and
mature hedgerows had higher rates of turnover than field margins
(Fig.~\ref{fig:beta}, estimate $\pm$ SE of the difference in turnover
between field margins and assembling hedgerows, $0.115 \pm 0.027$,
$p$-value=$0.0002$; field margins and mature hedgerows, $0.082 \pm
0.024$, $p$-value=$0.002$). The weighted interaction turnover at
assembling hedgerows, however, was not significantly higher than in
non-assembling, mature hedgerows.

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
Network nestedness significantly increased with assembly
(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
$\pm$ SE, $1.834 \pm 0.6142$, $p$-value=$0.022$). All of the networks
were significantly nested ($z$-scores $>$ 2,
Fig.~\ref{fig:baci}). Modularity decreased (Fig.~\ref{fig:baci}),
though the slope was not significantly different from
zero. % (estimate
% of the slope of modularity through time $\pm$ standard error of the
% estimate, $-0.524$ $\pm$ $0.295$, $p$-value=$0.124$).
In addition, none of the networks were significantly modular
($z$-scores $<$ 2, Fig.~\ref{fig:baci}). Connectance decreased as the
community assembled (Fig.~\ref{fig:baci}, estimate of the slope of
connectance through time $\pm$ standard error of the estimate,
$-0.0434$ $\pm$ $0.0152$, $p$-value=$0.03$). Specialization also
decreased, though the slope was only marginally significantly
different from zero (estimate of the slope of specialization through
time $\pm$ SE, $-0.926$ $\pm$ $0.450$, $p$-value=$0.078$). Most
communities were more generalized than expected when interactions were
randomized (Fig.~\ref{fig:baci}).

Both plant and pollinator species richness increased through time
(Fig.~\ref{fig:baci}, estimate of the slope of richness through time
$\pm$ SE, pollinators: $0.193$ $\pm$ $0.0729$, $p$-value=$0.008$;
plants: $0.212$ $\pm$ $0.0653$, $p$-value=$0.001$). Unsurprisingly,
pollinator species are colonizing and persisting at the assembling
hedgerows. Plant species richness in the networks is based on the
flowers actually visited by pollinators and not the presence of a
particular plant species at a site. Thus, though some new plant
species may establish themselves in the hedgerows, the increase in
plant richness in the networks is likely due to previously unvisited
plants attracting visitors as they mature and offer better rewards.

>>>>

We calculate species persistence as the proportion of surveys in which
a plant or pollinator is observed. Species observed consistently
within and between years are thus maximally persistent. Weighted
species degree is calculated from interaction observations from an
extensive dataset from Yolo County (approx.~18000 interaction records)
that included both the data included in this study and additional data
from sites where we collected flower visitors using the same methods
\citep{mgonigle-2015-x, ponisio2015farm}. To represent network
position variability, we computed the coefficient of variation of
weighted closeness centrality \citep{freeman1978centrality} at each
site through time. Closeness centrality represents the importance of a
space by calcuating the path lengths to other vertices (species) in
the network \citep{freeman1978centrality}. The shorter the mean path
length to other species, the higher the closeness centrality. We use
linear mixed models to test whether the species closeness variability
(log) is related to the persistence or degree of that species
\citep{lme4, lmetest}. We included random effects for species and
site. Because the degree and persistence of pollinators were strongly
correlated, ($\rho = 0.071$, $p$-value $<$ $2*10^{-16}$), we include
each explanatory variable in separate models. Plant degree and
persistence were not significantly correlated, but we use the same
models as we did for the pollinators for consistency.  Because an
approximately logarithmic increase in closeness centrality, as would
be expected with assembly by preferential attachment, would also lead
to high variability in closeness scores, we also test whether log
closeness centrality increases through time.

@@

In contradiction to the predictions of assembly by preferential
attachment, both pollinator persistence and degree were positively
related to network position variability (Fig.~\ref{fig:cv}, estimate
of the slope of closeness centrality variability and persistence $\pm$
standard error of the estimate, $0.496 \pm 0.182$, $p$-value=$0.016$;
slope of closeness centrality variability and degree, $0.004 \pm
0.002$, $p$-value=$0.056$). The slope of these relationships remained
significant when the species with the top $10$ persistence and degree
scores were dropped. In addition, plant persistence and degree were
not significantly related to network position variability
(Fig.~\ref{fig:cv}). % estimate of the slope of closeness variability and
% persistence $\pm$ SE, $-2.063 \pm 3.091$, $p$-value=$0.5$; slope of
% closeness variability and degree, $0.0018 \pm 0.002$,
% $p$-value=$0.3$).
The variability of species network position was not the result of
closeness linearly increasing through time, and, in fact, plant and
pollinator closeness decreased slightly through time (Fig.~S2,
estimate of the slope of closeness through time $\pm$ SE, pollinators:
$-0.082 \pm 0.021$, $p$-value=$0.003$; plants $-0.089 \pm
0.044$, $p$-value=$0.04$). Though statistically significant,
the models seems to be a poor fit to the data.

\subsection*{Species and interaction turnover}
The rates of plant, pollinator and interaction temporal turnover were
similar across assembling hedgerows, non-assembling hedgerows and
field margins, though mature hedgerows has marginally significantly
less pollinator turnover than field margins (Fig.~\ref{fig:beta},
estimate $\pm$ SE of the difference in turnover between field margins
and mature hedgerows, $-0.051 \pm 0.026$, $p$-value=$0.049$). The turnover of plants and interactions was not significantly different between site types. When
interactions where weighted by their similarity, both assembling and
mature hedgerows had higher rates of turnover than field margins
(Fig.~\ref{fig:beta}, estimate $\pm$ SE of the difference in turnover
between field margins and assembling hedgerows, $0.115 \pm 0.027$,
$p$-value=$0.0002$; field margins and mature hedgerows, $0.082 \pm
0.024$, $p$-value=$0.002$). The weighted interaction turnover at
assembling hedgerows, however, was not significantly higher than in
non-assembling, mature hedgerows.

\section*{Temporal changes in interaction patterns}
\subsection*{Network structure}
%Network nestedness significantly increased with assembly
%(Fig.~\ref{fig:baci}, estimate of the slope of nestedness through time
%$\pm$ SE, $1.834 \pm 0.6142$, $p$-value=$0.022$). 
Nestedness and modularity did not change in any predictable pattern with assembly (Fig.~\ref{fig:baci}). All of the networks were significantly nested ($z$-scores $>$ 2), but not modular ($z$-scores $<$ 2, Fig.~\ref{fig:baci}).

%though the slope was not significantly different from
%zero.(estimate
% of the slope of modularity through time $\pm$ standard error of the
% estimate, $-0.524$ $\pm$ $0.295$, $p$-value=$0.124$).
%In addition, none of the networks were significantly modular
% Fig.~\ref{fig:baci}).

Connectance decreased as the
community assembled (Fig.~\ref{fig:baci}, estimate of the slope of
connectance through time $\pm$ standard error of the estimate,
$-0.023$ $\pm$ $0.008$, $p$-value=$0.007$). Specialization also
decreased, though the slope was not significantly
different from zero. %(estimate of the slope of specialization through time $\pm$ SE, $-0.926$ $\pm$ $0.450$, $p$-value=$0.078$). 
Most communities were more generalized than expected when interactions were
randomized (Fig.~\ref{fig:baci}).

Both plant and pollinator species richness increased through time
(Fig.~\ref{fig:baci}, estimate of the slope of richness through time
$\pm$ SE, pollinators: $0.136$ $\pm$ $0.064$, $p$-value=$0.034$;
plants: $0.140$ $\pm$ $0.060$, $p$-value=$0.012$). Unsurprisingly,
pollinator species are colonizing and persisting at the assembling
hedgerows. Plant species richness in the networks is based on the
flowers actually visited by pollinators and not the presence of a
particular plant species at a site. Thus, though some new plant
species may establish themselves in the hedgerows, the increase in
plant richness in the networks is likely due to previously unvisited
plants attracting visitors as they mature and offer better rewards.
